Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-01-26 RR_manuscript/Draft_RR.Rmd
:memo: - add sim code to RR

```{r setup, include = FALSE}
knitr::opts_knit$set(root.dir = here::here())
library("papaja")
r_refs("r-references.bib")
library(tidyverse)
library(patchwork)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

@@

>>>>

```{r setup, include = FALSE}
knitr::opts_knit$set(root.dir = here::here())
library("papaja")
r_refs("r-references.bib")
library(tidyverse)
library(patchwork)
library(brms)
library(extraDistr)
```

```{r analysis-preferences}
my_seed <- 115116106
```

@@

```{r meta-bm}
set.seed(my_seed)
n <- 12
eta <- rnorm(n, 1, 0.5)
se <- rhcauchy(n, 0.1)
team <- letters[1:n]

eta_tbl <- tibble(
  eta,
  se,
  team
)

priors <- c(
  prior(normal(0, 1), class = Intercept),
  prior(cauchy(0, 1), class = sd)
)

meta_bm <- brm(
  eta | se(se) ~
    (1 | team),
  data = eta_tbl,
  prior = priors,
  chain = 1,
  seed = my_seed,
  file = here::here("RR_manuscript", "cache", "meta_bm")
)
```
